---
title: "Cross validation Demo"
output: html_document
date: '2022-07-25'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(glmnet)
```

## Goal

The goal of this demo is to see how exactly cross validation and lasso works. 


## Getting the data

Lets Read The data First 


```{r}

x <- read.table("geneExpressionData.csv")
y <- read.table("RA_Phen.csv")

```

##  Partitoning  Kfold data

Lets write a function to partition the data. Here we are partitioning the data into 10 folds.


```{r}


## Get the values for folds
GetFoldValue <- function(x,y,nfolds=10,lambdaVal=0.1){

suffle_id <- sample(nrow(x))   ## shuffle the data
Xs        <- x[suffle_id,]     ## order the x in shuffle order
Ys        <- y[suffle_id,]      ## order the y in shuffle order

reportFold <- NULL             ## create a matrix to save the fold data


folds <- cut(seq(1,nrow(x)),breaks=10,labels=FALSE)  ## create the folds
  
for(i in 1:nfolds){                                  
  
  testIndexes <- which(folds==i,arr.ind=TRUE)    ## seperate the test data
  XsTest <- Xs[testIndexes,]                     ## Get the test data for the Xs 
  YsTest <- Ys[testIndexes]                      ## Get the test data for the Ys
  
  XsTrain <- Xs[-testIndexes,]                   ## Get the train data for the Xs 
  YsTrain <- Ys[-testIndexes]                    ## Get the train data for the Ys
  
  
  model<- glmnet(                           ## for each fold train on train data
    XsTrain,
    YsTrain,
    family = c("gaussian"),
    alpha = 1,
    lambda = lambdaVal)
  
  YsTesthat  <- predict(model,                 ## Get the predicted values on test data
                        newx = as.matrix(XsTest),
                        type="response")
  
  res        <- cbind(YsTesthat,YsTest)
  reportFold <- rbind(reportFold,res)
  
  
  
}

return(reportFold)

}



```

## Replication

we are going to repeat the cross validation several times. This will insure that we are not getting anything by chance.

```{r}
PlotData <- NULL
lambda_seq <- seq(0,2,0.1)

for(lambdaVal in lambda_seq){

res <- sapply(1:100,function(nothing){res <- GetFoldValue(x,y,nfolds=10,lambdaVal=lambdaVal);
return(cor(res[,1],res[,2]))})


PlotData <- cbind(PlotData,res)

}


colnames(PlotData) <- lambda_seq
boxplot(PlotData,ylab="spearman correlation",xlab=expression(lambda))






```
